---
title: "logistic regression"
author: "Amira Ibrahim"
date: "September 5, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r dataset_for_logistic_homework_lec4, echo=TRUE}
library(readr)
Logestic_Data <- read.csv(file.choose(),header=TRUE)
```
#make sure that categorical variables read as a factor :
```{r , echo=TRUE}
Logestic_Data$outcome <- as.factor(Logestic_Data$outcome)
Logestic_Data$Treatment <- as.factor(Logestic_Data$Treatment)
Logestic_Data$SEX <- as.factor(Logestic_Data$SEX)
```

```{r , echo=TRUE}
library(dplyr)
logistic_regression <- Logestic_Data %>%
mutate( Outcome_dummy = (ifelse(outcome == "Success" , 1 , 0)), Treatment_dummy = (ifelse(Treatment == "Newdrug" , 1 , 0)), Sex_dummy = (ifelse(SEX == "Male" , 1 , 0)))
attach(logistic_regression)
```

##Check normality 
```{r , echo=TRUE}
library(moments)
skewness(HDL_LEVEL)
```
accepted range from -1 to +1 

```{r , echo=TRUE}
kurtosis(HDL_LEVEL)
```
accepted range from -2 to +2 , may to +3 

```{r , echo=TRUE}
boxplot(HDL_LEVEL~Treatment , xlab = "Treatment" , ylab = "HDL_Level" , main = "HDL_level acc to Treatment")
```
Visually , Data is normaly distributed

```{r , echo=TRUE}
shapiro.test(HDL_LEVEL)
```
P-value > 0.05 , so it is normally distributed

#test H0: No Change in HDL level according to Treatment :
```{r , echo=TRUE}
t.test(HDL_LEVEL~Treatment , mu = 0 , paired= FALSE , alternative= "two.sided" ,data=logistic_regression)
```
P-value > 0.05 , fail to reject H0

#Test H0 : No Diffrence in outcome Between Placebo & new drug
```{r , echo=TRUE}
chisq.test(table(outcome,Treatment))
```
p-value < 0.05 , Reject H0 

#Test H0 : Sex has no effect on outcome
```{r , echo=TRUE}
chisq.test(table(outcome,SEX))
```
P-value > 0.05 , Fail to reject H0

#Determination of correlation between treatment & outcome :
```{r , echo=TRUE}
cor(Outcome_dummy , Treatment_dummy , method = "spearman" )
```
It is +ve moderate correlated

##Find correlation between variables :
```{r , echo=TRUE}
correlations <- cor(logistic_regression[,4:7])
library(corrplot)
corrplot(correlations , method = "circle")
correlations
```
there is -ve weak correlation between sex & treatment

there is +ve weak correlation between HDL level & treatment

there is +ve moderate correlation between outcome & treatment

#Bad model in log regrission :
```{r , echo=TRUE}
badmodel <- glm(outcome~Treatment+SEX+HDL_LEVEL , family = "binomial" , data = logistic_regression)
summary(badmodel)
```

#determination of refrence value  : 
```{r , echo=TRUE}
logistic_regression <- within(logistic_regression,Treatment<-relevel(Treatment,ref="Placebo"))
goodmodel <-glm(outcome~Treatment+SEX+HDL_LEVEL , family = "binomial" , data = logistic_regression)
summary(goodmodel)
```

```{r , echo=TRUE}
exp(goodmodel$coefficients)
```

```{r , echo=TRUE}
library(Greg)
printCrudeAndAdjustedModel(goodmodel)[-1,]
```
#cruded value (the value of OR in the presence of other variables)
the odds of success for patient recieving newdrug taking the considration the sex and HDL level is 10.09

the odds of success for a male patient who is recieving newdrug and has HDL level is 2.33

the odds of success for a patient in the presence of  HDL level taking the considration the sex and receiving new drug is 1.10

#Adjusted values (the value of OR of variables without the presences of other variables)
the odds of the success for the patient recieving new drug is 10.88

the odds of the success for a male patient is 2.46

the odds of success for a patient with HDL level is 1.07



